Modeling Intervention Strategies for United States TB Control

### 2014-02-15 in_progress/presentations/paper/draft.tex
added table comment
Finished methods

\subsection{Agent Based}
The population level agent based model was implemented in several ways. Early
implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
implementations were constructed in $\texttt{C++}$. An implementation was made
that tracked the hill model exactly, up to still including the Acute Latent
compartment in the model. Probabilites of agent progression between various
health states were computed given rates in the hill model and a variety of
approximations. The model maintained scaled individual records for every
individual with LTBI, with susceptible individuals not modelled as agents.
Instead, a binomial distribution was used to probabilistically pick the number
of new infections each time step. Similarlly, immigration was also handeled
outside of the agent-based modelling. The final size standard deviation and
distribution data was collected via 2160 (MINUS SOME) runs with each agent in
the model truly representing one infected individual and a time step of $0.01$.
These data were analyzed in $R$. This model was also made to track deaths, total
TB cases, and infection sources. This data were consistent with the
deterministic model, and not reproduced in this write-up.

Further implementations of the \texttt{C++} model were made that deviated from
the basic Hill Model. Specifically, the acute latent compartment in the basic
Hill Model is a vestigal necessity of compartmental modeling and not reflective
of the biology of tuberculosis, and an agent based model was implemented that
more closely respects the biology of tuberculosis. Results from this model or
the strict Hill model did not differ significantly.

>>>>

\subsection{Agent Based}
The population level agent based model was implemented in several ways. Early
implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
implementations were constructed in $\texttt{C++}$. Probabilites of agent
progression between various health states were computed given rates in the hill
model and a variety of integration approximations. The model maintained
individual records for every individual with LTBI or active TB. Susceptible
individuals were not modelled as agents; instead, a binomial distribution was used to
probabilistically determine the number of new infections each time step.
Similarlly, the number of new immigrants each time step was chosen from a
probability distribution. We collected final population distribution data via
<+NUMBER OF RUNS 2160+> runs with each agent in the model truly representing one
infected individual and a time step of $0.01$.  These data were analyzed in $R$.
This model was also made to track deaths, total TB cases, and infection sources,
as well as economic data. These data were consistently normal and matched the
deterministic model.

Further implementations of the \texttt{C++} model were made that deviated from
the basic Hill Model. Specifically, the acute latent compartment in the basic
Hill Model is a vestigal necessity of compartmental modeling and not reflective
of the biology of tuberculosis. As such, an agent based model was implemented
that more closely respects the biology of tuberculosis. Results from this model
were also normal and did not differ significantly from the strict Hill model.
